Automated Topic Naming

### 2011-09-05 ese/ese.tex
exp1 pgsql resultsd
exp1 to exp3 postgresql updates

\todo{this discussion is about which DB? where do the numbers come from?}
For \textsf{exp1} the labels with the most topics
were
\emph{correctness} (182 topics) and \emph{testability} (121). 
We did not see many results for \emph{usability} or \emph{accuracy}, which were associated with fewer than ten topics. 
We also looked for correlations between our labels: excluding double matches (self-correlation), our highest co-occurring terms were \emph{verifiability}
with \emph{traceability}, and \emph{testability} with \emph{correctness} (76 and 62 matches, respectively).
% See the following sections for our error analysis.

For \textsf{exp2}, there are more unnamed topics than \textsf{exp1}. 
Only \emph{reliability} produces a lot of matches, mostly with the word ``error''. 
Co-occurrence results were poor. This suggests our word lists were overly restrictive.

For \textsf{exp3}, we generally labelled more topics. 
As we mentioned, the word-lists are broad, so there are likely to be false-positives (discussed below). 
The most frequent label, 265 topics, was \emph{usability}, and the
least frequent label, 44 topics, was \emph{maintainability}. 
Common co-occurrences were \emph{reliability} with \emph{usability}, \emph{efficiency} with \emph{reliability}, and \emph{efficiency} with \emph{usability}
(200, 190, and 150 topics in common, respectively).

@@

Because our ground truth annotations were relevant only to ISO9126,
we estimate that \textsf{exp1} had poor
performance via the overlap between ISO9126 and the Kayed ontology.
For \textsf{exp1} the F-measures for MaxDB were from $0$ to $0.18$ with an average
of $0.03$, and for MySQL were from $0$ to $0.16$ with an average of
$0.05$.
\todo{update these numbers but from where? }
% 0.177215189873 / 6
% .02953586497883333333
% (0.0298507462687 + 0.0661157024793 + 0.0634920634921 + 0 + 0.115384615385) / 6
% .04580718793751666666

>>>>

%\DONE{this discussion is about which DB? where do the numbers come from?}
For \textsf{exp1} the labels with the most topics
were
\emph{correctness} (182/305/748 topics) and \emph{testability} (121/238/625). 
We did not see many results for \emph{usability} (4/0/138) or
\emph{accuracy} (3/0/27), which were associated with fewer than ten topics. 
We also looked for correlations between our labels: excluding double
matches (self-correlation), our highest co-occurring terms were
\emph{verifiability} or \emph{correctness}
with \emph{traceability}, and \emph{testability} with \emph{correctness} (76 and 62 matches, respectively).
% See the following sections for our error analysis.

For \textsf{exp2}, there are more unnamed topics than \textsf{exp1}. 
Only \emph{reliability} produces the most matches, mostly due to the word ``error''. 
Co-occurrence results were poor. This suggests our word lists were overly restrictive.
For PostgreSQL \emph{reliability} and  \emph{usability} co-occurred
with \emph{portability} and \emph{efficiency}.

For \textsf{exp3}, we generally labelled more topics. 
As we mentioned, the word-lists are broad, so there are likely to be false-positives (discussed below). 
The most frequent label across all projects was \emph{usability}, and the
least frequent label was \emph{maintainability}. 
Common co-occurrences were \emph{reliability} with \emph{usability}, \emph{efficiency} with \emph{reliability}, and \emph{efficiency} with \emph{usability}.
%(200, 190, and 150 topics in common, respectively).

@@

Because our ground truth annotations were relevant only to ISO9126,
we estimate that \textsf{exp1} had poor
performance via the overlap between ISO9126 and the Kayed ontology.
For \textsf{exp1} the F-measures for MaxDB were from $0$ to $0.18$ with an average
of $0.03$, for MySQL were from $0$ to $0.16$ with an average of
$0.05$, and for PostgreSQL $0$ to $0.15$ with an average of $0.07$.

%\todo{update these numbers but from where? }
% 0.177215189873 / 6
% .02953586497883333333
% (0.0298507462687 + 0.0661157024793 + 0.0634920634921 + 0 + 0.115384615385) / 6
% .04580718793751666666

% pgsql
% portability 
% 0.0910746812386
% efficiency 
% 0.154639175258
% reliability
% 0.0470588235294
% maintainability
% 0
% usability
% 0.0720720720721
%> v <- c(0.0910746812386 , 0.154639175258 , 0.0470588235294 , 0 , 0.0720720720721)
%> summary(v)
%   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
%0.00000 0.04706 0.07207 0.07297 0.09107 0.15460
